---
title: "MA615 Assignment 2"
author: "Chen Xu U49903384"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
pacman::p_load("knitr","ggplot2","rstanarm","tidyr","dplyr")
```

```{r, fig.width=12,fig.height=10}
source("wrangling_code.R")
source("visualization_function.R")
```

##What my assignment analysis
I selected three datasets from Gapminder
1. The employment rate for females age above 15 years old
2. The mean years in school for females who age from 15 years old to 24 years old
3. The mean years in school for females who age above 25 years old

Firstly I added dataset 2 and 3 to get a new dataset: The mean years in school for females who age above 15 years old. After doing this, I can get the same range for age of my two subsets.
Secondly, I chose 12 counties: 4 developed countries, 4 development countries and 4 relatively poor development countries.
4 developed countries: The United States, The United Kingdom, Japan and Russia
4 development countries: China, Mexico, Indonesia and Brazil
4 relatively poor development countries: India, Nigeria, Bangladesh and Pakistan
to anaylsis the relationship between female's employment rate and female's educated level of different countries.
And analysis the datas from 1990 to 2008.

##What I found during my analysis
As we can see from the first plot, we can see that if we exclude China, when female can get more time to study in school, the employment rate for female will going up. And what I found very interesting is that female's education level is related to the development level for a country. As we can see, it is very clear that females older than 15 in 4 relatively poor development countries seldom can have more than 10 years educational experience, females in 4 development countries can have 10-20 years educational experience, while females in 4 developed countries can all get more than 20 years educational experience. 
When it comes to my second plot, we can see more clearly that the employment rate is going up from relatively poor development countries to developed countries.
And another interesting relationship I found is that in Asian countries like China, Japan, India and Indonesia. While the mean years females spent in school are getting more and more from 1990 to 2008, the employment rate had a trend to going down. this relationship reminds me of 1997 Asian financial crisis and Financial crisis of 2007–2008. Besides these two reasons, the rapid population growth of Asian countries during this period may be another important reason for the continued decline in employment.
